Glucose ingestion before and after resistance training does not augment ribosome biogenesis in healthy moderately trained young adults

### 2024-01-09 manuscript_revised.RMD
added reference to tab 3

Glucose ingestion before and after RT sessions did not generally improve skeletal muscle recovery throughout the intervention, neither during the intervention in a rested state (Figure 1D, 23hrs after exercise; Post 2RT: -0.02 ± 0.05 vs. -0.04 ± 0.03 *p* = `r pdiff.c2`, Post 4RT: -0.02 ± 0.05 vs. -0.06 ± 0.03 *p* = `r pdiff.c3`, glucose vs. placebo), nor acutely after the sixth and final RT-session (30min post 6RT: -0.03 ± 0.05 vs. -0.09 ± 0.06 *p* = `r pdiff.c5`, 2h post 6RT: -0.02 ± 0.07 vs. -0.08 ± 0.07 *p* = `r pdiff.c6`, glucose vs. placebo) or in a rested state after the sixth RT session (23h post 6RT: -0.05 ± 0.06 vs. -0.09 vs. 0.05 *p* = `r pdiff.c7`, glucose vs. placebo). Glucose ingestion before and after RT compared to placebo was associated with a 7% less reduction in strength after five RT sessions (Figure 1D, -0.06 ± 0.06 vs -0.14 ± 0.12 *p* = `r pdiff.c4`, glucose vs. placebo).

Both RT with glucose and placebo led to significantly reduced strength after the fifth session compared to baseline, by 11 and 18% respectively (Figure 1D, Post 5RT: *p* = 0.000). Comparisons of the acute data gathered from after five sessions until and including 23 hours after the sixth session showed an average increase in strength of 5-9% from RT with glucose and placebo 30 minutes after the sixth RT session (Figure 1D, 30min post 6RT: *p* = `r apc2`) and two hours after the sixth RT session (Figure 1D, 2h post 6RT: *p* = `r apc3`). Twenty-three hours after the last (sixth) RT session, strength was unchanged compared to after the fifth RT session (Figure 1D, 23h post 6RT: *p* = `r apc4`).

@@

###### Baseline tab
#
#
## Author: KL
#
#
## Purpose:

@@

### Primer sequence table

@@

>>>>

Glucose ingestion before and after RT sessions did not generally improve skeletal muscle recovery throughout the intervention, neither during the intervention in a rested state (Figure 1D, 23hrs after exercise; Post 2RT: *p* = `r pdiff.c2`, Post 4RT: *p* = `r pdiff.c3`), nor acutely after the sixth and final RT-session (30min post 6RT: *p* = `r pdiff.c5`, 2h post 6RT: *p* = `r pdiff.c6`) or in a rested state after the sixth RT session (23h post 6RT: *p* = `r pdiff.c7`). Glucose ingestion before and after RT compared to placebo was associated with a 7% less reduction in strength after five RT sessions (Figure 1D, *p* = `r pdiff.c4`).

Both RT with glucose and placebo led to significantly reduced strength after the fifth session compared to baseline, by 11 and 18% respectively (Figure 1D, Post 5RT: *p* = 0.000). Comparisons of the acute data gathered from after five sessions until and including 23 hours after the sixth session showed an average increase in strength of 5-9% from RT with glucose and placebo 30 minutes after the sixth RT session (Figure 1D, 30min post 6RT: *p* = `r apc2`) and two hours after the sixth RT session (Figure 1D, 2h post 6RT: *p* = `r apc3`). Twenty-three hours after the last (sixth) RT session, strength was unchanged compared to after the fifth RT session (Figure 1D, 23h post 6RT: *p* = `r apc4`). Table 3 shows the mean change in absolute peak torque values per condition and angular velocity.

@@

@@

@@

**Table 3. Peak Torque** Mean peak torque per condition and angular velocity measured at the different times during the intervention. Baseline = before exercise, After 2RT = 23 hours after two training sessions, After 4RT = 23 hours after four training sessions, After RT5 = 23 hours after five training sessions, After 6RT#1 = 30min after the sixth training session, After 6RT#2 = 2 hours after the sixth training session, After 6RT#3 = 23 hours after the sixth training session. Values are reported as mean ± SD. * = significant difference between glucose and placebo.

```{r humac table, echo = FALSE}

# Baseline data
humac.clean2 <- readRDS("./data/data-gen/humac/humac.clean2.RDS")

# Pre-post five sessions data

isometric <- readRDS("./data/data-gen/humac/isom.absolutechange.RDS")
iso60 <- readRDS("./data/data-gen/humac/iso60.absolutechange.RDS")
iso240 <- readRDS("./data/data-gen/humac/iso240.absolutechange.RDS")

# Pre-post session six data (acute data)
isometric.acute <- readRDS("./data/data-gen/humac/isom.absolutechange.ac.RDS")
iso60.acute <- readRDS("./data/data-gen/humac/iso60.absolutechange.ac.RDS")
iso240.acute <- readRDS("./data/data-gen/humac/iso240.absolutechange.ac.RDS")

## Summarising

# Wide format

tabdat <- humac.clean2 |>
  select(subject, supplement, time, acute, measure = test, peak.torque) %>%
#  filter(time == "baseline" & acute == "rest") |>
  group_by(measure, supplement, time) |>
  summarise(mean.pt = mean(peak.torque),
            sd.pt = sd(peak.torque)) |>
  mutate(mean = paste0(sprintf("%.1f",mean.pt), " (", sprintf("%.1f",sd.pt), ")")) |>
  select(supplement, time, measure, mean) |>
  mutate(supplement = if_else(supplement == "glucose",
                       "Glucose",
                       if_else(supplement == "placebo",
                               "Placebo", supplement))) |>
  mutate(measure = if_else(measure == "isom",
                           "0\U00BA sec",
                           if_else(measure == "isok.60",
                                   "60\U00BA sec",
                                   if_else(measure == "isok.240",
                                           "240\U00BA sec", measure)))) |>
  pivot_wider(names_from = time,
              values_from = mean)

## Making the table

humac.flex <- tabdat |>
  flextable() |>
  compose(i = 1, j = c(1, 2, 3, 4, 5, 6, 7, 8, 9), part = "header",
          value = c(as_paragraph("Condition"),
                    as_paragraph("Velocity"),
                    as_paragraph("Baseline"),
                    as_paragraph("After 2RT"),
                    as_paragraph("After 4RT"),
                    as_paragraph("After 5RT"),
                    as_paragraph("After 6RT#1"),
                    as_paragraph("After 6RT#2"),
                    as_paragraph("After 6RT#3"))) |>
  add_body_row(values = c(" ", "Knee-extension peak torque (Nm)"), colwidths = c(2, 7))

humac.flex <- border(humac.flex, 
                     i = NULL,
                     j = NULL,
                     border = NULL,
                     border.top = fp_border_default(color = "black"),
                     border.bottom = fp_border_default(color = "black"),
                     border.left = fp_border_default(color = "black"),
                     border.right = fp_border_default(color = "black"),
                     part = "all")

humac.flex <- footnote(humac.flex,
                       i = 4,
                       j = 6,
                       as_paragraph("Sig. difference"),
                       ref_symbols = "*",
                       part = "body", inline = TRUE)

humac.flex
